Dissertation

### 2023-11-14 Manuscript/Appendix/IGAS-Supplemental.qmd
move appendix

```{r, include=FALSE, echo=FALSE}
source(here::here('Functions/IGAS_ProcessFunctions.R'))
library(patchwork)
#rm(list=ls())
###### data loading and organization #######

@@

### exponential learning models fit to individual subjects
```{r}

@@

h4<-e2TestFits %>% ggplot(aes(x=positionX,y=pRate,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ggtitle("Learning rates ")+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+ylab("Inverse Learning Rate")+xlab("Testing Location")
h4

@@

### First vs. second half of testing stage
```{r}

@@

h1=testSplit %>% filter(testHalfSbj=="1st-Half") %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
 geom_bar(aes(group=conditType,fill=conditType),stat="summary",position=dodge,fun="mean")+stat_summary(aes(x=positionX,group=conditType),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+
 scale_y_continuous(name="Mean Absolute Deviation From Target",limits=c(0,400))+ 
 ggtitle("Testing Performance - 1st half")+
  ylab("Mean Absolute Deviation From Target")+xlab("Testing Location")+theme(legend.position="none")

h2=testSplit %>% filter(testHalfSbj=="2nd-Half") %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
 geom_bar(aes(group=conditType,fill=conditType),stat="summary",position=dodge,fun="mean")+stat_summary(aes(x=positionX,group=conditType),fun.data=mean_se,geom="errorbar",position=dodge,width=.8) + 
 scale_y_continuous(name="",limits=c(0,400))+ 
 ggtitle("Testing Performance - 2nd half")+
  xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+
  guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)

@@

h3 <- tsw %>% ggplot(aes(x=positionX,y=endMinusStart))+
  geom_bar(aes(group=conditType,fill=conditType),stat="summary",position=dodge,fun="mean")+
  stat_summary(aes(x=positionX,group=conditType),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+
  ylab("2nd Half Deviation - 1st Half Deviation")+ 
  ggtitle("Improvement Per Testing Location")+
  xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+
  guides(fill=guide_legend(title="Testing Location"))+theme(legend.position="none")

@@

(h1 + h2) / (h3 + h4)

>>>>

```{r, setupP1_A, include=FALSE}
here::set_here(path='..')
source(here::here('Functions/IGAS_ProcessFunctions.R'))
library(patchwork)
#rm(list=ls())
###### data loading and organization #######

@@

### exponential learning models fit to individual subjects
```{r}
#| label: fig-igas-a1

@@

# h4<-e2TestFits %>% ggplot(aes(x=positionX,y=pRate,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ggtitle("Learning rates ")+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+ylab("Inverse Learning Rate")+xlab("Testing Location")
# h4

@@

### First vs. second half of testing stage
```{r}
#| fig.height: 8 
#| fig.width: 10

@@

h1=testSplit %>% filter(testHalfSbj=="1st-Half") %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
 geom_bar(aes(group=conditType,fill=conditType),stat="summary",position=dodge,fun="mean")+stat_summary(aes(x=positionX,group=conditType),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+
 scale_y_continuous(name="Mean Absolute Deviation From Target",limits=c(0,400))+ 
 ggtitle("Testing - 1st half")+
  ylab("Mean Absolute Deviation From Target")+xlab("Testing Location")+theme(legend.position="top")

h2=testSplit %>% filter(testHalfSbj=="2nd-Half") %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
 geom_bar(aes(group=conditType,fill=conditType),stat="summary",position=dodge,fun="mean")+
  stat_summary(aes(x=positionX,group=conditType),fun.data=mean_se,geom="errorbar",position=dodge,width=.8) + 
 scale_y_continuous(name="",limits=c(0,400))+ 
 ggtitle("Testing - 2nd half")+
  xlab("Testing Location")+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position="top") +
  guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)

@@

h3 <- tsw %>% ggplot(aes(x=positionX,y=endMinusStart))+
  geom_bar(aes(group=conditType,fill=conditType),stat="summary",position=dodge,fun="mean")+
  stat_summary(aes(x=positionX,group=conditType),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+
  ylab("2nd Half Deviation - 1st Half Deviation")+ 
  ggtitle("Improvement Per Location")+
  xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+
  guides(fill=guide_legend(title="Testing Location")) +theme(legend.position="none")

@@

#(h1 + h2) / (h3)

(h1+h2)/h3
